\TITLE

### 2023-03-21 paper/content.tex
move footnotes to references

Also, our protocol does not provide its own dispute-resolution mechanism as Themis does. However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party. 
It can be instantiated with either the local court or police, or one of the blockchain
dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, a hybrid blockchain application development platform for securing, verifying, and exchanging enterprise information, https://lto.network/, (last visited Jan. 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

@@

However, our use case is different in that the physical materials are transfered from the (anonymous) customer to the (public) SP. This, allows for siplification of the delivery process. We assume that there is a way to anonymously deliver a package without revealing the customer personal information either via SP's drop box, Parcel Locker services (e.g. Amazon Locker, InPost\footnote{InPost, Parcel locker service, \url{https://inpost.pl/en}, \LASTVISITED}), a customer's trusted party, of even post office.

@@

Themis~\cite{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web. Themis
resolve disputes by a set of voluntary anonymous mediators participating
in voting and deciding whether a party misbehaved. The honesty of
mediators is achieved by the monetary incentivization and reputation
system.

@@

Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\footnote{IronFish, The Privacy Platform
for web3, \url{https://ironfish.network}, \LASTVISITED} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).

Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi\footnote{Wasabi Wallet, Open-source, non-custodial Bitcoin Wallet for desktop, \url{https://wasabiwallet.io/}, (last visited Nov. 28, 2022)} (via CoinJoin \cite{maxwellCoinJoinBitcoinPrivacy2013}).

@@

\item separate address: each transaction uses an unique address associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets (BIP-32)\footnote{Bitcoin Improvement Proposals, Hierarchical Deterministic Wallets, \url{https://github.com/bitcoin/bips/blob/master/bip-0032.mediawiki}, (last visited Dec. 03, 2022)} and published on message board, to achieve non-repudiation.
\item memo: the payments are sent to sigle SP account, but contain an extra field named ``memo'' filled with the unique indentifier $\textrm{provisionID}$. 
\end{itemize}

@@

In case of a dispute, there must be a way to prove to justice that the customer has paid for the transaction. As the proof of payment is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains. Monero allows proving and checking payments via dedicated API\footnote{Monero, How to prove payment, \url{https://www.getmonero.org//resources/user-guides/prove-payment.html}, \LASTVISITED}. ZCash provides a mechanism called Payment Disclosure \footnote{Gareth Davies, An Introduction to Payment Disclosure in Zcash, \url{https://garethtdavies.medium.com/an-introduction-to-payment-disclosure-in-zcash-96748c209d49}, \LASTVISITED}. We call the proof of payment a \textit{payment recepit}.

@@

\item Anonymous payments: Monero \cite{vansaberhagenCryptoNote2013}, ZCash
  \cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin \cite{fuchsbauerAggregateCashSystems2019},
  Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
\item Message board: Open timestamps\footnote{Open timestamps, A timestamping proof standard, \url{https://opentimestamps.org}, \LASTVISITED}, Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Bitcoin blockchain (Proof of Existence~\footnote{Proof of existence, An online service to prove the existence of documents, \url{https://docs.proofofexistence.com}, \LASTVISITED}, Chainpoint~\footnote{Chainpoint, Blockchain Proof and Anchoring Standar, \url{ https://chainpoint.org/}, \LASTVISITED}), Ethereum blockchain, or any other public blockchain that supports attaching extra data along the transaction.
\item Storage network: IPFS \cite{benetIPFSContentAddressed2014}, Filecoin
  \cite{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
  Swarm\cite{teamSWARMStorageCommunication2021}.
\end{enumerate}

@@

\noindent \textbf
{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS\footnote{IPFS, Content addressing and CIDs, \url{https://docs.ipfs.tech/concepts/content-addressing}, (last visited Dec. 01, 2022)}. However, since our protocol does not depend on this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.

@@

\begin{itemize}
  \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
  \item{Storage netowork} — we use the Powergate\footnote{Powergate, \url{https://github.com/textileio/powergate}, (last visited Dec. 20, 2022)}, which is a wrapper around Filecoin and IPFS.
  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, Truffle Ganache\footnote{Truffle Ganache, \url{https://trufflesuite.com/ganache/}, (last visited Dec. 20, 2022)} and Solidity language.
  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React}\footnote{React, A JavaScript library for building user interfaces, \url{https://reactjs.org}, (last visited Dec. 20, 2022)} for creating UI, and \texttt{web3.js}\footnote{web3.js, A JavaScript library for building on Ethereum, \url{https://web3js.org}, (last visited Dec. 20, 2022)} for interaction with Ethereum. We use \texttt{MetaMask}\footnote{MetaMask, A crypto wallet \& gateway to blockchain apps, \url{https://metamask.io}, (last visited Dec. 20, 2022)} browser extension for signing and submitting transactions to Ethereum's node. We use \texttt{monerod}\footnote{Monero, The Monero daemon \texttt{monerod}, \url{https://monerodocs.org/interacting/monerod-reference/}, (last visited Dec. 20, 2022)} network client and \texttt{monero-wallet-cli}\footnote{Monero, The CLI client for Monero, \url{https://monerodocs.org/interacting/monero-wallet-cli-reference/}, (last visited Dec. 20, 2022)} command-line interface for interacting with Monero blockchain.
\end{itemize}

@@

The customer gets some testing Monero funds using faucet service\footnote{Monero, faucet, \url{https://community.rino.io/faucet/stagenet/}, \LASTVISITED}.

@@

\paragraph{Provable Results Availability}
Content addressable networks such as IPFS can not guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage. In case of dispute, the SP can upload the content again, proving its availability. The SP has no motivation to proceed with this kind of misbehavior other than putting the customer in a disadvantaged position caused by the lost dispute.}. However, the Filecoin network, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content\footnote{Filecoin, Slashing, \url{https://docs.filecoin.io/storage-provider/rewards/slashing}, (last visited Jan. 03, 2023)})~\cite{protocollabsFilecoinDecentralizedStorage2017}.

@@

The cost of gas is denominated in $\mathrm{ETH}$. The price of gas at the time of the experiment (Jan. 03, 2023) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$\footnote{Etherscan, Ethereum Gas Tracker, \url{https://etherscan.io/gastracker}, (last visited Jan. 03, 2023)}, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.

@@

Centralized justice is the biggest obstacle in achieving a system that complies with Web 3.0 postulates\footnote{Web3, \url{https://en.wikipedia.org/wiki/Web3}, (last visited Jan. 05, 2023)}.

The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court\footnote{Aragon Court, Decentralized Dispute Resolution Protocol, https://aragon.org/aragon-court, (last visited Jan. 10, 2023)}, LTO Network\footnote{LTO Network, a hybrid blockchain application development platform for securing, verifying, and exchanging enterprise information, https://lto.network/, (last visited Jan. 17, 2023)}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.

@@

\subsection{Self-sovereign identities}
Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer's personal information. For example, in Poland, all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\footnote{Regulation of the Minister of Health of March 23, 2006, on quality standards for medical diagnostic and microbiological laboratories, \url{https://isap.sejm.gov.pl/isap.nsf/DocDetails.xsp?id=WDU20060610435}}.

>>>>

Also, our protocol does not provide its own dispute-resolution mechanism as Themis does. However, we assume the existence of an abstract justice that accepts evidence and punishes the misbehaving party. 
It can be instantiated with either the local court or police, or one of the blockchain
dispute resolution services like Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B,ltonetworkOnchainIdentitiesCredentials}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}.

@@

However, our use case is different in that the physical materials are transfered from the (anonymous) customer to the (public) SP. This, allows for siplification of the delivery process. We assume that there is a way to anonymously deliver a package without revealing the customer personal information either via SP's drop box, Parcel Locker services (e.g. Amazon Locker, InPost~\cite{inpostParcelLockerService}), a customer's trusted party, of even post office.

@@

Themis~\cite{mengThemisDecentralizedEscrow2019} besides providing fair exchange protocol,
also offers a semi-autonomous decentralized dispute resolution system that complies with the Web3 postulates of a decentralized web~\cite{ethereumWhatWeb3Why}. Themis resolve disputes by a set of voluntary anonymous mediators participating in voting and deciding whether a party misbehaved. The honesty of mediators is achieved by the monetary incentivization and reputation system.

@@

Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\cite{ironfishPrivateAnonymousEasy} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).

Overly techniques that achieve anonymity on top of non-privacy-preserving blockchains are: Ethereum's Tornado Cash~\cite{pertsevTornadoCashPrivacy2019} (via zkSNARK~\cite{grothSizePairingbasedNoninteractive2016} and MiMC~\cite{albrechtMiMCEfficientEncryption2016}), Bitcoin's Wasabi~\cite{wasabiwalletBitcoinPrivacyWallet} (via CoinJoin~\cite{maxwellCoinJoinBitcoinPrivacy2013}).

@@

\item separate address: each transaction uses an unique address associated with the transaction. Such addresses can be derived using Hierarchical Deterministic Wallets~\cite{wuilleBIP32HierarchicalDeterministic2012} and published on message board, to achieve non-repudiation.
\item memo: the payments are sent to sigle SP account, but contain an extra field named ``memo'' filled with the unique indentifier $\textrm{provisionID}$. 
\end{itemize}

@@

In case of a dispute, there must be a way to prove to justice that the customer has paid for the transaction. As the proof of payment is trivial in transparent and trackable blockchains, it gets more complicated when it comes to anonymous blockchains. Monero allows proving and checking payments via dedicated API~\cite{moneroHowProvePayment}. ZCash provides a mechanism called Payment Disclosure~\cite{daviesIntroductionPaymentDisclosure2017}. We call the proof of payment a \textit{payment recepit}.

@@

\item Anonymous payments: Monero \cite{vansaberhagenCryptoNote2013}, ZCash
  \cite{ben-sassonZerocashDecentralizedAnonymous2014}, Grin \cite{fuchsbauerAggregateCashSystems2019},
  Tornado Cash \cite{pertsevTornadoCashPrivacy2019}.
\item Message board: Open timestamps~\cite{opentimestampsTimestampingProofStandard}, Stampery \cite{crespoStamperyBlockchainTimestamping2017}, Bitcoin blockchain (Proof of Existence~\cite{proofofexistenceWebApplicationProve}, Chainpoint~\cite{chainpointBlockchainProofAnchoring}), Ethereum blockchain, or any other public blockchain that supports attaching extra data along the transaction.
\item Storage network: IPFS~\cite{benetIPFSContentAddressed2014}, Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, or Ethereum's
  Swarm~\cite{teamSWARMStorageCommunication2021}.
\end{enumerate}

@@

\noindent \textbf
{Content Identifier (cid)}\label{content-identifier-cid} is a term coined by IPFS~\cite{ipfsContentIdentifiersCIDs}. However, since our protocol does not depend on this particular implementation of the storage network, we let the $\mathrm{cid}$ be any other identifier that securely and uniquely points to the content.

@@

\begin{itemize}
  \item{Anonymous payments} — we use the Monero blockchain \cite{noetherRingSignatureConfidential2015}.
  \item{Storage netowork} — we use the Powergate~\cite{textilePowergate2023}, which is a wrapper around Filecoin and IPFS.
  \item{Message board} — we use the Ethereum blockchain \cite{woodEthereumSecureDecentralised2014}; concretely, its local development version Truffle Ganache and Solidity language.
  \item{Customer and SP} — we create client side web application (webapp) using \texttt{React.js} for creating UI, and \texttt{web3.js} library for interaction with Ethereum. We use \texttt{MetaMask} browser extension for signing and submitting transactions to Ethereum's node. We use \texttt{monerod} network client and \texttt{monero-wallet-cli} command-line interface for interacting with Monero blockchain.
\end{itemize}

@@

The customer gets some testing Monero funds using faucet service~\cite{rinoMoneroStagenetFaucet}.

@@

\paragraph{Provable Results Availability}
Content addressable networks such as IPFS can not guarantee the availability of the content\footnote{Nothing prevents the SP from publishing the result, receiving the $\mathrm{cid}$, publishing $\mathrm{PoP}$, and immediately after removing the result from the local storage. In case of dispute, the SP can upload the content again, proving its availability. The SP has no motivation to proceed with this kind of misbehavior other than putting the customer in a disadvantaged position caused by the lost dispute.}. However, the Filecoin~\cite{protocollabsFilecoinDecentralizedStorage2017}, which works as an incentivization layer on top of IPFS, increases the content availability via economic incentivisation (i.e., punishment in case of lack of proof of storage of the content~\cite{filecoinSlashing}).

@@

The cost of gas is denominated in $\mathrm{ETH}$. The price of gas at the time of the experiment (Jan. 03, 2023, \url{https://etherscan.io/gastracker}) was $0.000000002227 \frac{\mathrm{ETH}}{\mathrm gas}$, and the price of 1 $\mathrm{ETH}$ was $1261.97 \mathrm{USD}$.

@@

Centralized justice is the biggest obstacle in achieving a system that complies with Web3 postulates~\cite{ethereumWhatWeb3Why}.

The possible directions for mitigation of such issues are to either (i) replace local justice with blockchain dispute resolution systems like those proposed in Themis~\cite{mengThemisDecentralizedEscrow2019}, Kleros~\cite{bergollaKlerosSociolegalCase2022,gudkovCrowdArbitrationBlockchain2020}, Aragon Court~\cite{aragonDecentralizedDisputeResolution}, LTO Network~\cite{ltonetworkNextGenBlockchainB2B}, and other Online Dispute Resolution platforms~\cite{allenGovernanceBlockchainDispute2019}; or (ii) make it infeasible to provide incorrect results.

@@

\subsection{Self-sovereign identities}
Our research in the field showed that some jurisdictions require SPs to associate the diagnosis with the customer's personal information. For example, in Poland, all laboratories performing medical diagnostic tests, and collecting the material (except tests for HIV) are obligated to the unambiguous identification and verification of the identity of the patient from whom the material was collected~\cite{ministerstwozdrowiaRegulationMinisterHealth2006}.
